An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2021-07-29 paper.tex
extended section intro

\clearpage
\section{Background}
We first give a short introduction to implicit parametric models and likelihood-free inference. We then provide the necessary background on two of these methods: Optimisation Monte Carlo (OMC) and its recent robust generalisation, robust OMC (ROMC).
%\input{latex_files/ch2/2_1_implicit_models}

>>>>

\clearpage
\section{Background}
We first give a short introduction to implicit parametric models and
likelihood-free inference. We then focus on the methods relevant for
this paper: first the earlier Optmisation Monte Carlo (OMC) and then
its recent robust generalisation, robust OMC, for which we provide the
software package as part of the Engine for likelihood-free inference
(ELFI), a larger inference platform that we briefly introduce at the
end of this background section.

%\input{latex_files/ch2/2_1_implicit_models}
